Refinements for Open Automata

### 2023-06-23 2021-Refinement/paper/refinementarticleV2.tex
ref

The simulation  ensures the preservation of   
safety properties as deadlock-freeness  and, more generally, 
all linear temporal logic properties in the sense of \cite{Abrialbooks96,Kouchnarenko:2007} \LUDO{\st{add ref sur ``simulation  ensures the preservation of  safety properties'' pas sur temporal logic!}}.  Our focus is about the properties of simulation, in particular closure properties such as preservation under composition. Some works   have addressed the problem of non-introduction of blocking by composition. For example,  \cite{DIHEGO2020110598}  presented a refinement relation on process algebra based on failure semantics that is basically different from the (bi)simulation \cite{10.5555/640428.640430}.   \LUDO{the last sentence is not really informative} \LUDO{how do we compare our work?}

>>>>

The simulation  ensures the preservation of   
safety properties as deadlock-freeness  and, more generally, 
all linear temporal logic properties \cite{Abrialbooks96,Kouchnarenko:2007}.  Our focus is about the properties of simulation, in particular closure properties such as preservation under composition. Some works   have addressed the problem of non-introduction of blocking by composition. For example,  \cite{DIHEGO2020110598}  presented a refinement relation on process algebra based on failure semantics that is basically different from the (bi)simulation \cite{10.5555/640428.640430}.   \LUDO{the last sentence is not really informative} \LUDO{how do we compare our work?}
